Simulation Figures for Genome Biology (simulations)

### 2018-07-23 datasets/GWAS/GWAS.Rmd
Set random seed for uninformative covariate
Change 'scott' labels to 'fdrreg'

```{r}
bmi <- bmi %>% mutate(ind_covar_uninf = rnorm(nrow(bmi)))
```

@@

```{r}
bd <- addBMethod(bd, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

>>>>

```{r}
set.seed(39580)
bmi <- bmi %>% mutate(ind_covar_uninf = rnorm(nrow(bmi)))
```

@@

```{r}
bd <- addBMethod(bd, "fdrreg-t",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "fdrreg-e",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

### 2018-07-23 datasets/RNA-Seq/RNAseq-gtex.Rmd
Change 'scott' labels to 'fdrreg'

    bd <- addBMethod(bd, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))

   bd <- addBMethod(bd, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))

@@

ash was the method that rejected the largest number of hypotheses, followed by lfdr and scott-theoretical.

>>>>

    bd <- addBMethod(bd, "fdrreg-t",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))

   bd <- addBMethod(bd, "fdrreg-e",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))

@@

ash was the method that rejected the largest number of hypotheses, followed by lfdr and fdrreg-theoretical.

### 2018-07-23 datasets/RNA-Seq/RNAseq-mir200c.Rmd
Change 'scott' labels to 'fdrreg'

As a second RNA-seq dataset, we will test for differences in gene expression upon the knockout of the microRNA mir-200c [(Kim et al., 2013)](https://doi.org/10.1038/nsmb.2701).  The raw fastq files can be found under the accession number `SRP030475`. As the number of samples is limited the experiment might be underpowered, as in most RNA-seq analysis. This is an experimental scenario that could benefit from power gained using modern FDR control methods.

>>>>

As a second RNA-seq dataset, we will test for differences in gene expression upon the knockout of the microRNA mir-200c [(Kim et al., 2013)](http://dx.doi.org/10.1038/nsmb.2701).  The raw fastq files can be found under the accession number `SRP030475`. As the number of samples is limited the experiment might be underpowered, as in most RNA-seq analysis. This is an experimental scenario that could benefit from power gained using modern FDR control methods.

### 2018-07-23 datasets/RNA-Seq/yeast-simulation.Rmd
Change 'scott' labels to 'fdrreg'

```{r}
bd <- initializeBenchDesign()
bd <- addBMethod(bd, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

>>>>

```{r}
bd <- initializeBenchDesign()
bd <- addBMethod(bd, "fdrreg-t",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "fdrreg-e",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

### 2018-07-23 datasets/simulations/simulations-informative-cosine.Rmd
Change 'scott' labels to 'fdrreg'

```{r}
bdplus <- bd
bdplus <- addBMethod(bdplus, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bdplus <- addBMethod(bdplus, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

>>>>

```{r}
bdplus <- bd
bdplus <- addBMethod(bdplus, "fdrreg-t",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bdplus <- addBMethod(bdplus, "fdrreg-e",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

### 2018-07-23 manuscript_figures/manuscript_figures.Rmd
Change 'scott' labels to 'fdrreg'

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder) +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.96, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

@@

## specify method order
method_order <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
objdat_joint <- dplyr::mutate(objdat_joint, method = factor(method, levels = c(method_order, "Total Tests")))
```

@@

# methods that use a covariate
cov.methods <- c("ihw", "bl", "lfdr", "scott-empirical", "scott-theoretical")

@@

rowOrder <- c("ihw", "bl", "lfdr", "scott-empirical", "scott-theoretical")

>>>>

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "fdrreg-e", "fdrreg-t", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder) +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.96, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

@@

## specify method order
method_order <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "fdrreg-e", "fdrreg-t", "ashq")
objdat_joint <- dplyr::mutate(objdat_joint, method = factor(method, levels = c(method_order, "Total Tests")))
```

@@

# methods that use a covariate
cov.methods <- c("ihw", "bl", "lfdr", "fdrreg-e", "fdrreg-t")

@@

rowOrder <- c("ihw", "bl", "lfdr", "fdrreg-e", "fdrreg-t")

### 2018-07-23 manuscript_figures/manuscript_figures_sims.Rmd
Change 'scott' labels to 'fdrreg'

methodset <- c("bonf", "bh", "ihw", "qvalue", "bl-df03", "lfdr",
               "scott-empirical", "scott-theoretical", "ashq")
```

@@

For null simulations, rather than the false discovery rate, we take a look at the true negative
rate (equivalently, the proportion of false positives) since the FDR will be 1 if any rejections
are made. Additionally, we take a look at the FWER (the proportion of simulation replicates out
of 100 with at least one rejection). In these plots, `ashq`, `scott-theoretical` and `scott-theoretical`
are excluded for the Chi-Squared simulation settings.

```{r, fig.width = 18, fig.height = 8}
res_nullset <- dplyr::filter(res, setting == "null",
                             !(Method == "ashq" & grepl("chi\\^2", dist)),
                             !(grepl("scott", Method) & grepl("chi\\^2", dist)))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)

>>>>

methodset <- c("bonf", "bh", "ihw", "qvalue", "bl-df03", "lfdr",
               "fdrreg-e", "fdrreg-t", "ashq")
```

@@

For null simulations, rather than the false discovery rate, we take a look at the true negative
rate (equivalently, the proportion of false positives) since the FDR will be 1 if any rejections
are made. Additionally, we take a look at the FWER (the proportion of simulation replicates out
of 100 with at least one rejection). In these plots, `ashq`, `fdrreg-e` and `fdrreg-t`
are excluded for the Chi-Squared simulation settings.

```{r, fig.width = 18, fig.height = 8}
res_nullset <- dplyr::filter(res, setting == "null",
                             !(Method == "ashq" & grepl("chi\\^2", dist)),
                             !(grepl("fdrreg", Method) & grepl("chi\\^2", dist)))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)
